Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
table 2 explain

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.
\begin{table*}
\centering
\begin{tabular}{lc}
\hline 
\textbf{Reducer Node} & \textbf{Description} \\
Geometry Nodes &\\
\hline
InputMesh & Loads shape to which materials will be assigned\\\
Stratum & Divides an input volume into an outer layer of given thickness and an interior blob\\
Column & Divides an input volume into a number of columns\\
\hline
Material Nodes &\\
\hline
ConstantMaterial & Assigns a constant material to an input volume \\
LayeredMaterial &  Assigns a layered set of materials to an input volume \\
QuadLayerMaterial & ??? \\
SubdivSurfMateral & ??? \\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}

@@

\subsection{Refractive Caustics}
We have also implemented two algorithms for computing goal-based caustics;  ~\cite{Marios:2011} and ~\cite{Finckh:2010}.
The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image. The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface. Of note is the fact that this algorithm does not quire a simulation algorithm. Despite this it is still implementable within our framework.

>>>>

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.
\begin{table*}
\centering
\begin{tabular}{lc}
\hline 
\textbf{Reducer Node} & \textbf{Description} \\
Geometry Nodes &\\
\hline
InputMesh & Loads shape to which materials will be assigned\\\
Stratum & Divides an input volume into an outer layer of given thickness and an interior blob\\
Column & Divides an input volume into a number of columns\\
\hline
Material Nodes &\\
\hline
ConstantMaterial & Assigns a constant material to an input volume \\
LayeredMaterial &  Assigns a layered set of materials to an input volume \\
QuadLayerMaterial & Like LayeredMaterial, but the materials are separated by a quadrangle\\
SubdivSurfMateral & Like LayeredMaterial, but the materials are separated by a subdivision surface \\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}

@@

\subsection{Refractive Caustics}
We have also implemented two algorithms for computing goal-based caustics;  ~\cite{Marios:2011} and ~\cite{Finckh:2010}.
The first version of this algorithm computes  a set of micro-lenses which produce the desired caustic image. 
The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface.
Each tuner is connected to its four neighbors.
During the execution of an individual tuner, the optimization algorithm makes a randomized decision about
 whether or not to swap its micro-lens with one of its neighbors.
The tuners are run in sequence until some convergence criteria is met.
Of note is the fact that this algorithm does not quire a simulation algorithm. 
Despite this it is still implementable within our framework.
